Optimizing httk's 3comp2 model

### 2025-07-08 data-raw/optimizing_httk_model.Rmd

```{r}
load_dawson2021()
schems <- httk::get_cheminfo("dtxsid", species = "rat",
                             model = "3compartment2") |>
  suppressWarnings()

@@

>>>>

```{r}
load_dawson2021()
schems <- httk::get_cheminfo("dtxsid", species = "rat",
                             model = "gas_pbtk") |>
  suppressWarnings()

@@

Initial test with regular models.

```{r}
test_pk2 <- pk(data = minicvt) + 
  stat_error_model(error_group = vars(Chemical, Species)) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE)

test_pk2 <- do_data_info(test_pk)
test_pk2 <- do_prefit(test_pk)
test_fit2 <- do_fit(test_pk, n_cores = 4)
winmodel2 <- get_winning_model(test_fit)
